Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
section 4

%-------------------------------
\subsection{Abstract acceleration of linear dynamics} 
\label{ssec:aa}
%-------------------------------

@@

An overview of the algorithm for controller synthesis is given in
Fig.~\ref{fig:CEGIS-precision-increment}.  One important observation is that
we verify and synthesize a controller over $k$ time steps.  We~then compute
a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03}
for this controller, and verify correctness for $\overline{k}$ time steps. 
Essentially, $\overline{k}$ is the number of iterations required to
sufficiently unwind the closed-loop state-space system, 
which ensures that the boundaries are not violated for any other $k{>}\overline{k}$.

@@

Next, we describe the different phases in Fig.~\ref{fig:CEGIS-precision-increment}
(blocks 1 to 4) in detail.

>>>>

%-------------------------------
\subsection{Abstract acceleration of linear dynamics \note{Shall we move the material on AAccel to the Preliminaries?}} 
\label{ssec:aa}
%-------------------------------

@@

An overview of the algorithm for controller synthesis is given in Fig.~\ref{fig:CEGIS-precision-increment}.  
One important observation is that we verify and synthesize a controller over a finite number ($k$) of time steps.  
We then compute a completeness threshold $\overline{k}$~\cite{DBLP:conf/vmcai/KroeningS03} 
for this controller, and verify correctness for $\overline{k}$ time steps. 
As we will later argue, $\overline{k}$ is the number of iterations required to sufficiently unwind the closed-loop state-space model,  
ensuring that the boundaries are not violated for any other $k{>}\overline{k}$.

@@

Next, we describe in detail the different phases in Fig.~\ref{fig:CEGIS-precision-increment} (blocks 1 to 4).
